### 2020-02-02 thesis/paper.tex
structure sample text

\part{Theory}

@@

A lot of research as been put toward the topic of clustering, resulting in a large number of different methods. \cite{surveyclustering}

\section{Visual Clustering Frameworks}

@@

\section{Consensus Clustering}

consensus cluster plus \cite{10.1093/bioinformatics/btq170}

\chapter{Methods}

@@

\part{Implemented Tool}
\chapter{Using the Tool}\label{cha:Tool}
This chapter describes what a user can do with the newly implemented tool.

@@

\part{Testing}
\chapter{Experiments}\label{cha:experiments}
\section{Solutions better than Base-Clusterings}
bla

>>>>

@@

A lot of research as been put toward the topic of clustering, resulting in a large number of different methods. \cite{surveyclustering}
%only brief explanation on the development of clustering algorithms and groups
\section{Visual Clustering Frameworks}

@@

\section{Consensus Clustering}
%eplanation of consensus clustering and groups 
bla

%also tools for consensus clustering
consensus cluster plus \cite{10.1093/bioinformatics/btq170}

\part{Theory}
\chapter{Methods}
The newly created tool uses a large amount of existing methods which are described in this chapter.

@@

\part{Implemented Tool}
\chapter{Using the Tool}\label{cha:Tool}
%maybe not "this chapter..."
This chapter describes what a user can do with the newly implemented tool.

@@

\part{Testing}
\chapter{Experiments}\label{cha:experiments}
To show the value of the new tool different scenarios created. The goals of the tool are to improve on the ease of finding complex cluster structures and improve on the result in comparison to only using simple clustering methods. Another aim is to visualize the data and clustering results such that an expert user can make a well informed decision on which solutions best fit the data.
\section{Solutions better than Base-Clusterings}
bla
